### 2016-05-25 R/ITHIM.Rmd
Added install_github to ITHIM.Rmd

```{r libs, eval = TRUE, echo = FALSE, results = "hide", warning = FALSE, error = FALSE}
options(repos='http://cran.rstudio.com/')
library("ggplot2")
library("reshape2")
library("plyr")
library("ITHIM")
```

>>>>

```{r libs, eval = TRUE, echo = TRUE, results = "hide", warning = FALSE, error = FALSE, message = FALSE}
options(repos='http://cran.rstudio.com/')
library("ggplot2")
library("reshape2")
library("plyr")
library("devtools")
install_github("syounkin/ITHIM")
```
